### 2016-03-16 Manuscript/SW_early_life_telomeres_SOM.Rmd
Discussion and fogure edits

```{r Table S2}
temp <- Loss

#Run the model
lm1 <- lmer(TROC ~ Agemonths * (Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ + Season) + (1|LayYear),
            data = temp,
            REML = FALSE)
lm1 <- standardize(lm1)

@@

tableS2 <- data.frame(Model = apply(t1,1,getterms,c(2:16)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(tableS2) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(tableS2) <- NULL
tableS2$Model[tableS2$Model == ''] <- 'Null model'
tableS2[,3:5] <- lapply(tableS2[,3:5],as.numeric)
kable(tableS2,digits=2)

>>>>

```{r Table S2}
temp <- subset(Loss,Agemonths == 1)

#Run the model
lm1 <- lmer(Loss ~ (Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ + Season) + (1|LayYear),
            data = temp,
            REML = FALSE)
lm1 <- standardize(lm1)

@@

tableS2 <- data.frame(Model = apply(t1,1,getterms,c(2:8)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(tableS2) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(tableS2) <- NULL
tableS2$Model[tableS2$Model == ''] <- 'Null model'
tableS2[,3:5] <- lapply(tableS2[,3:5],as.numeric)
kable(tableS2,digits=2)

### 2016-03-16 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Discussion and fogure edits

temp <- dd
temp$Agemonths[temp$Agemonths>10] <- '12+'
temp$Agemonths <- factor(temp$Agemonths,levels = c('1','6','10','12+'))

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  geom_jitter(col='grey') +
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none')+
  geom_boxplot(outlier.colour=NA,alpha = 0.2)+
  annotate('text',x = 0.6,y = 2.1,label = 'A')

temp <- Loss
temp$Agemonths <- factor(temp$Agemonths)

Fig1B <- ggplot(temp,aes(x = Agemonths,y = TROC))+
  geom_jitter(col='grey') +
  ylab('Loss in RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none')+
  geom_boxplot(outlier.colour=NA,alpha = 0.2)+
  annotate('text',x = 0.6,y = 2.1,label = 'B')

Fig1C <- ggplot(temp,
       aes(x = LayYear,
           y = RTL)) +
  ylab('RTL') + 
  xlab('') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60,size = 14,vjust=0.5), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_jitter(col = 'grey')+
  geom_boxplot(outlier.colour = NA,alpha = 0.2)+
  scale_x_discrete(limits = factor(1998:2014),drop=F)+
  annotate('text',x = 1,y = 2.1,label = 'C')

pdf('Figures/Figure 1.pdf',
    width = 6,
    height = 6,
    paper = 'a4r')
multiplot(Fig1A,Fig1B,Fig1C,layout=matrix(c(1,2,3,3),nrow = 2,byrow=T))
dev.off()

@@

@@

#Sort out row/col names
nams <- rownames(table2)
nams[nams == 'z.NonHelper'] <- 'Non helpers'
nams[nams == 'c.Sex'] <- 'Sex'
nams[nams == 'z.TQ'] <- 'TQ'
nams[nams == 'c.Helper'] <- 'Helpers'
nams[nams == 'z.BodyMass'] <- 'Body mass'
nams[nams == 'z.Agemonths'] <- 'Age'
nams[nams == 'z.Tarsus'] <- 'Tarsus'
nams[nams == 'c.Season'] <- 'Season'
nams[nams == 'c.Season:z.Agemonths'] <- 'Age x season'
nams[nams == 'z.Agemonths:z.NonHelper'] <- 'Age x non helpers'
nams[nams == 'c.Sex:z.Agemonths'] <- 'Age x sex'
nams[nams == 'z.Agemonths:z.TQ'] <- 'Age x TQ'
nams[nams == 'c.Helper:z.Agemonths'] <- 'Age x helpers'
nams[nams == 'z.Agemonths:z.BodyMass'] <- 'Age x mass'
nams[nams == 'z.Agemonths:z.Tarsus'] <- 'Age x tarsus'

@@

Fig2A <- forestplot(table2)+
  annotate('text',x = 1,y = 0.25,label = 'A')

@@

Fig2B <- ggplot(temp,
       aes(x = factor(Agemonths),
           y = RTL,
           fill=Season)) +
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_jitter(aes(colour = Season),position=position_jitterdodge(dodge.width = 0.8))+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))+
  annotate('text',x = 0.55,y = 2.1,label = 'B')

Fig2C <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           colour=`Age (months)`,
           fill = `Age (months)`,
           shape = `Age (months)`)) +
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(alpha = 0.2)+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c(grey(0.2),'darkorange','darkgreen'))+
  scale_fill_manual(values = c('darkgrey','darkorange','darkgreen'))+
  annotate('text',x = 17,y = 2.1,label = 'C')

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 9,
    paper = 'a4r')
multiplot(Fig2A,Fig2B,Fig2C,layout = matrix(c(1,1,2,3),nrow = 2,byrow = T))
dev.off()

@@

temp <- Loss

#####################
#3A
#####################

#Run the model
lm2 <- lmer(TROC ~ Agemonths * (Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ + Season) + (1|LayYear),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

#Sort out row/col names
nams <- rownames(table2)
nams[nams == 'z.NonHelper'] <- 'Non helpers'
nams[nams == 'c.Sex'] <- 'Sex'
nams[nams == 'z.TQ'] <- 'TQ'
nams[nams == 'c.Helper'] <- 'Helpers'
nams[nams == 'z.BodyMass'] <- 'Body mass'
nams[nams == 'z.Agemonths'] <- 'Age'
nams[nams == 'z.Tarsus'] <- 'Tarsus'
nams[nams == 'c.Season'] <- 'Season'
nams[nams == 'c.Season:z.Agemonths'] <- 'Age x season'
nams[nams == 'z.Agemonths:z.NonHelper'] <- 'Age x non helpers'
nams[nams == 'c.Sex:z.Agemonths'] <- 'Age x sex'
nams[nams == 'z.Agemonths:z.TQ'] <- 'Age x TQ'
nams[nams == 'c.Helper:z.Agemonths'] <- 'Age x helpers'
nams[nams == 'z.Agemonths:z.BodyMass'] <- 'Age x mass'
nams[nams == 'z.Agemonths:z.Tarsus'] <- 'Age x tarsus'

@@

Fig3A <- forestplot(table2)+
  annotate('text',x = 1,y = 0.45,label = 'A')

temp <- Loss

Fig3B <- ggplot(temp,
       aes(x = factor(Agemonths),
           y = TROC,
           fill=Season)) +
  ylab('Loss in RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_jitter(aes(colour = Season),position=position_jitterdodge(dodge.width = 0.8))+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))+
  annotate('text',x = 0.55,y = 2.1,label = 'B')

Fig3C <- ggplot(temp,
       aes(x = Tarsus,
           y = TROC,
           col=`Age (months)`)) +
  ylab('Loss in RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(alpha = 0.2)+
  stat_smooth(method = 'lm')+
    scale_colour_manual(values = c(grey(0.2),'darkorange','darkgreen'))+
  scale_fill_manual(values = c('darkgrey','darkorange','darkgreen'))+
  annotate('text',x = 20,y = 2.1,label = 'C')

pdf('Figures/Figure 3.pdf',
    width = 8,
    height = 9,
    paper = 'a4r')
multiplot(Fig3A,Fig3B,Fig3C,layout = matrix(c(1,1,2,3),nrow = 2,byrow = T))
dev.off()

>>>>

temp <- dd

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 1,y = 2.1,label = 'A')

temp <- subset(dd,DeltaAge !=0)

Fig1B <- ggplot(temp,aes(x = DeltaAge,y = RTL))+
  ylab('RTL') + 
  xlab(expression(Delta*' age (months)')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = -100,y = 2.1,label = 'B')

pdf('Figures/Figure 1.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig1A,Fig1B,layout=matrix(c(1,2),nrow = 2,byrow=T))
dev.off()

@@

Fig2A <- ggplot(temp,aes(x = LayYear,y = RTL,col=Season,fill=Season))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top')+
  geom_jitter(aes(colour = Season),position=position_jitterdodge(dodge.width = 0.8))+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))+
  annotate('text',x = 1,y = 2.1,label = 'A')

temp <- juv
x <- ifelse(temp$Season == 'Winter',0.5,0)
temp$LayYear2 <- temp$LayYear+x
temp <- temp[!(duplicated(temp$LayYear2)),]

Fig2B <- ggplot(temp,aes(x = LayYear2,y = Density))+
  ylab('Adult population size') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none')+
  geom_line(stat = 'identity')+
  annotate('text',x = 1998,y = 360,label = 'B')

Fig2C <- ggplot(temp,
       aes(x = Density,
           y = RTL,
           colour=Season,
           fill = Season)) +
  ylab('RTL') + 
  xlab('Adult population size') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none') +
  geom_point()+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 240,y = 2.1,label = 'C')

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig2A,Fig2B,Fig2C,layout=matrix(c(1,1,2,3),nrow = 2,byrow=T))
dev.off()

@@

#Sort out row/col names
nams <- rownames(table2)
nams[nams == 'z.NonHelper'] <- 'Non helpers'
nams[nams == 'c.Sex'] <- 'Sex (males)'
nams[nams == 'z.TQ'] <- 'TQ'
nams[nams == 'c.Helper'] <- 'Helpers'
nams[nams == 'z.BodyMass'] <- 'Body mass'
nams[nams == 'z.Agemonths'] <- 'Age'
nams[nams == 'z.Tarsus'] <- 'Tarsus'
nams[nams == 'c.Season'] <- 'Season (winter)'
nams[nams == 'c.Season:z.Agemonths'] <- 'Age x season'
nams[nams == 'z.Agemonths:z.NonHelper'] <- 'Age x non helpers'
nams[nams == 'c.Sex:z.Agemonths'] <- 'Age x sex'
nams[nams == 'z.Agemonths:z.TQ'] <- 'Age x TQ'
nams[nams == 'c.Helper:z.Agemonths'] <- 'Age x helpers'
nams[nams == 'z.Agemonths:z.BodyMass'] <- 'Age x mass'
nams[nams == 'z.Agemonths:z.Tarsus'] <- 'Age x tarsus'

@@

Fig3A <- forestplot(table2)+
  annotate('text',x = 1,y = 0.25,label = 'A')

@@

Fig3B <- ggplot(temp,
       aes(x = `Age (months)`,
           y = RTL,
           fill=Season)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_jitter(aes(colour = Season),position=position_jitterdodge(dodge.width = 0.8))+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))+
  annotate('text',x = 0.55,y = 2.1,label = 'B')

Fig3C <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           colour=`Age (months)`,
           fill = `Age (months)`,
           shape = `Age (months)`)) +
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c(grey(0.2),'darkorange','darkgreen'))+
  scale_fill_manual(values = c('darkgrey','darkorange','darkgreen'))+
  annotate('text',x = 17,y = 2.1,label = 'C')

Fig3D <- ggplot(temp,
       aes(x = `Age (months)`,
           y = RTL,
           fill=Sex)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_jitter(aes(colour = Sex),position=position_jitterdodge(dodge.width = 0.8))+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))+
  annotate('text',x = 0.55,y = 2.1,label = 'D')

pdf('Figures/Figure 3.pdf',
    width = 9,
    height = 9,
    paper = 'a4r')
multiplot(Fig3A,Fig3B,Fig3C,Fig3D,layout = matrix(c(1,1,1,2,3,4),nrow = 2,byrow = T))
dev.off()

@@

```{r Figure 4}

temp <- Loss
temp[,'Age (months)'] <- factor(temp$Agemonths)
temp$LayYear <- factor(temp$LayYear)

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 0,y = 2.1,label = 'A')

temp2 <- temp
temp2$TimeDiff <- temp2$TimeDiff/365

Fig4B <- ggplot(temp2,
       aes(x = TimeDiff,
           y = Loss,
           colour=`Age (months)`,
           fill = `Age (months)`)) +
  ylab(expression(Delta*'RTL')) + 
  xlab('Time (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(alpha=0)+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c(grey(0.2),'darkorange','darkgreen'))+
  scale_fill_manual(values = c('darkgrey','darkorange','darkgreen'))+
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  coord_cartesian(ylim = c(-0.5,0.25))+
  annotate('text',x = 0,y = 0.5,label = 'B')

pdf('Figures/Figure 4.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig4A,Fig4B,layout=matrix(c(1,2),nrow=2,byrow=T))
dev.off()

```{r Figure 5}

#####################
#4A
#####################
temp <- subset(Loss,Agemonths == 1)
#Run the model
lm2 <- lmer(Loss ~ (Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ) + (1|LayYear),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

#Model averaging
lm3 <- dredge(lm2)
lm3 <- subset(lm3,delta <=6)
lmavg <- model.avg(lm3,fit=T)
myimp <- importance(lmavg)

@@

#Sort out row/col names
nams <- rownames(table2)
nams[nams == 'z.NonHelper'] <- 'Non helpers'
nams[nams == 'c.Sex'] <- 'Sex'
nams[nams == 'z.TQ'] <- 'TQ'
nams[nams == 'c.Helper'] <- 'Helpers'
nams[nams == 'z.BodyMass'] <- 'Body mass'
nams[nams == 'z.Agemonths'] <- 'Age'
nams[nams == 'z.Tarsus'] <- 'Tarsus'
nams[nams == 'c.Season'] <- 'Season'

@@

Fig4 <- forestplot(table2)

pdf('Figures/Figure 4.pdf',
    width = 5,
    height = 4,
    paper = 'a4')
Fig5
dev.off()
